SMT-Boosted Security Types for Low-Level MPC

### 2024-10-11 esop25/metalang.tex
checkpoint

\begin{proof}
  Given the assumptions, suppose that $E_1' \not\models E_2'$
  is an $\alpha$-renaming of $E_1 \models E_2$. In this
  case the consequence follows immediately. Otherwise,
  suppose on the contrary we can witness
  $E_1' \not\models E_2'$. By definition this means that
  $E_1' \wedge \neg E_2'$ is satisfiable
  but $E_1 \wedge \neg E_2$ is not, which is a contradiction
  by Lemma \ref{lemma-eqs-notg}. \qed 
\end{proof}

>>>>

\begin{proof}
  Given the assumptions, suppose that $E_1' \not\models E_2'$
  is an $\alpha$-renaming of $E_1 \models E_2$. In this
  case the consequence follows immediately. Otherwise,
  suppose on the contrary we can witness
  $E_1' \not\models E_2'$. By definition this means that
  $E_1' \wedge \neg E_2'$ is satisfiable
  but $E_1 \wedge \neg E_2$ is not, which is a contradiction
  by Lemma \ref{lemma-fresh}. \qed 
\end{proof}
